---
title: "Perceived Diversity in the Comic Book Community"
author: "Emily Jennings-Dobbs"
date: "4/20/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

***Data cleanup***

```{r}
#read in data
library(readxl)
df <- read_excel("C:\\\\Users\\\\emily\\\\OneDrive\\\\Desktop\\\\temp\\\\Perceived Diversity in the Comic Book Community (Responses).xlsx")


head(df)
```
```{r}

#turn table into data frame
library(tidyverse)

df <- as.data.frame(df, stringsAsFactors = TRUE)

#remove timestamp
df <- df[,-1]
head(df)


#calculate involvement score
df <- df %>% mutate(involvement_sum = involvement_base + readership + comic_cons + comic_talk + comic_shops + cosplay)

hist(df$involvement_sum, breaks = 40, xlab = "involvement score", main = NULL)

```
A sum of all involvement scores is used as an overall score of involvement in the comic book community.

```{r}
#create dataframe without invalid expected age
alt_df <- df %>% filter(nchar(expected_age)<=2) %>% mutate(expected_age = as.numeric(expected_age))
head(alt_df)

#remove excess factors
for(i in 1:51){
  if(alt_df[i, "gender"]!= "Female" && alt_df[i, "gender"]!= "Male"){
    alt_df[i, "gender"]="Other"
  }
}

for(i in 1:51){
  if(alt_df[i, "race"]!= "White" && alt_df[i, "race"]!= "Hispanic or Latino"  && alt_df[i, "race"]!= "Black or African American"){
    alt_df[i, "race"]="Other"
  }
}

for(i in 1:51){
  if(alt_df[i, "expected_race"]!= "White" && alt_df[i, "expected_race"]!= "Hispanic or Latino"  && alt_df[i, "expected_race"]!= "Black or African American"){
    alt_df[i, "expected_race"]="Other"
  }
}
```




***Graphs ***



```{r}
df_factor <- alt_df %>%
  mutate_if(sapply(alt_df, is.character), as.factor)



library(cowplot)
my_plots <- lapply(names(df_factor), function(var_x){
  p <- 
    ggplot(df_factor) +
    aes_string(var_x)

  if(is.numeric(df_factor[[var_x]])) {
    p <- p + geom_density(color="purple4", fill="lavender")

  } else {
    p <- p + geom_bar(color="purple4", fill="lavender")  + scale_fill_discrete(drop=TRUE)
  } 
})

plot_grid(plotlist = my_plots[1:4])
plot_grid(plotlist = my_plots[5:10])
plot_grid(plotlist = my_plots[11:15])
plot_grid(plotlist = my_plots[16:19])
plot_grid(plotlist = my_plots[20:29])

```
***Personality Variables***

```{r}
personality_df <- df %>% dplyr::select(shy_outgoing, inside_outside, logic_emotion, alonetime_withothers, responsibility, playsafe_risks, imagination, apathetic_empathetic, groupwork_individual, self_discipline)

p_values <- matrix(nrow = ncol(personality_df), ncol = 2)

row.names(p_values) <- colnames(personality_df)
colnames(p_values) <- c("p_value", "Decision")

for (i in 1:ncol(personality_df)) {
  y <- t.test(personality_df[,i], mu = 3.5) 
  p_values[i,1] <- y$p.value
  
  if(p_values[i,1] >= .05){
    p_values[i,2] <- "fail to reject"
  }else{
    p_values[i,2] <- "reject"
  }
}

knitr::kable(as.data.frame(p_values), "markdown")
rm(p_values)

```

Only personality traits that are significantly different to the proposed value are playsafe-risks, apathetic-empathetic, and self-discipline. This group believes people in the commic book community to be risk takers, empathetic, and self-disciplined. 

```{r}

library(ggplot2)
df %>%
  keep(is.numeric) %>%                     # Keep only numeric columns
  gather() %>%                             # Convert to key-value pairs
  ggplot(aes(value)) +                     # Plot the values
    facet_wrap(~ key, scales = "free") +   # In separate panels
    geom_density()                         # as density
```

***Expectation & Acceptance T-tests***
```{r}
#50.8% of people are women
table(df$expected_gender)

```
54/67 believed the average person in the comic book community was male

```{r}
binom.test(54,67,p = .492)
```
An exact binomial test gives us a p-value of 2.16e-07 which is well below .05, so we reject the NULL hypothesis that people expect about half the population of the comic book community and instead believe men to make up between 69% to 89% of the population.

```{r}
table(df$expected_race)
```
According to cencus data 76.5% of the US population is white.
```{r}
binom.test(62,67,p = .765)
```
62 out of 67 people think the average person in the comic community is white. This is significantly larger than the proportion of white people in the US. 


***Correlational Study***

```{r}
personality_cor <- cor(df %>% dplyr::select(shy_outgoing, inside_outside, logic_emotion, alonetime_withothers, responsibility, playsafe_risks, imagination, apathetic_empathetic, groupwork_individual, self_discipline))
  


Acceptance_cor <- cor(df %>% dplyr::select(acceptance_men, acceptance_women, acceptance_LGBT, acceptance_POC))



library(corrplot)

#correlation plot of acceptance questions
corrplot(Acceptance_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

#correlation plot of personality questions
corrplot(personality_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

```{r}


numeric_df <- df %>% keep(is.numeric)


p_values <- matrix(nrow = ncol(numeric_df), ncol = 3)

row.names(p_values) <- colnames(numeric_df)
colnames(p_values) <- c("p_value", "Decision", "correlation")

for (i in 1:ncol(numeric_df)) {
  y <- cor.test(numeric_df[,i] ,df$age, method = "pearson")

  p_values[i,1] <- y$p.value
  
  if(p_values[i,1] >= .05){
    p_values[i,2] <- "fail to reject"
  }else{
    p_values[i,2] <- "reject"
  }
  
  p_values[i,3] <- y$estimate
}

knitr::kable(as.data.frame(p_values), "markdown")
```
```{r}
t.test(df$acceptance_men, df$acceptance_women)
```
```{r}
#better plots
library(ggpubr)

#demographics vs expectation
  #age vs expectation (age, race, gender, education)
  aea <- ggplot(alt_df, aes(age, expected_age)) + geom_point()
  aer <- ggplot(df, aes(age)) + geom_histogram() + facet_wrap(~expected_race)
  aeg <- ggplot(df, aes(age)) + geom_histogram() + facet_wrap(~expected_gender)
  aee <- ggplot(df, aes(age)) + geom_histogram() + facet_wrap(~expected_education)
  ggarrange(aea, aer, aeg, aee) 
  
  #gender vs expectation
  gea <- ggplot(alt_df, aes(x=expected_age)) + geom_histogram() + facet_wrap(~gender)
  ger <- ggplot(alt_df, aes(x = gender)) + geom_bar() + facet_wrap(~expected_race)
  geg <- ggplot(alt_df, aes(gender)) + geom_bar() +facet_wrap(~expected_gender)
  gee <- ggplot(alt_df, aes(gender)) + geom_bar() +facet_wrap(~expected_education)
  
  ggarrange(gea, ger, geg, gee)
  
  #education vs expectation
  eee <- ggplot(df, aes(education)) + geom_bar() +facet_wrap(~expected_education)
  eer <- ggplot(alt_df, aes(x = education)) + geom_bar() + facet_wrap(~expected_race)
  eeg <- ggplot(alt_df, aes(education)) + geom_bar() +facet_wrap(~expected_gender)
  eea <- ggplot(alt_df, aes(x=expected_age)) + geom_histogram() + facet_wrap(~education)
  
  ggarrange(eee, eer, eeg, eea)
  
#demographics vs Involvement

ig <- ggplot(df, aes(involvement_sum)) + geom_histogram() + facet_wrap(~gender)
ie <- ggplot(df, aes(involvement_sum)) + geom_histogram() + facet_wrap(~education)
ir <- ggplot(df, aes(involvement_sum)) + geom_histogram() + facet_wrap(~race)

ggarrange(ig, ie, ir)
```

```{r}
#median age is 38.2

t.test(alt_df$expected_age, mu = 38.2)
```
```{r}
alt_df %>% 
  dplyr::select(gender, involvement_sum,shy_outgoing, inside_outside, logic_emotion, alonetime_withothers, responsibility, playsafe_risks, imagination, apathetic_empathetic, groupwork_individual, self_discipline ) %>%
  gather(-involvement_sum, -gender, key = "var", value = "value") %>%
  ggplot(aes(x = value, y = involvement_sum, color = gender)) +
    geom_point() +
    facet_wrap(~ var, scales = "free") +
    theme_bw() +
    scale_color_manual(values=c("blue4", "darkmagenta", "firebrick3"))
```
```{r}
alt_df %>% 
  dplyr::select(gender, involvement_sum, age, education, race, acceptance_men, acceptance_women, acceptance_LGBT, acceptance_POC, expected_age, expected_race, expected_gender, expected_education  ) %>%
  gather(-involvement_sum, -gender, key = "var", value = "value") %>%
  ggplot(aes(x = value, y = involvement_sum, color = gender)) +
    geom_point() +
    facet_wrap(~ var, scales = "free") +
    theme_bw() +
    scale_color_manual(values=c("blue4", "darkmagenta", "firebrick3"))

```
